The language of generalization: Probability, vagueness, and interaction

### 2018-10-08 paper/comgen-paper.Rmd

header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{amsmath}
  - \usepackage{graphicx}
  - \usepackage{subcaption}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}

@@

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
```

>>>>

header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{amsmath}
  - \usepackage{graphicx}
  - \usepackage{subcaption}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{xcolor}

@@

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)
```
